Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
restructure "Setting up models" paragraph

\paragraph{Setting up models and feeding them data.}
%
Models in scikit-learn, called \emph{estimators}, are objects
instantiated with all parameters that describe them, but with data. They
have a {\tt fit} method, that accepts an $(n \times p)$ data matrix,
$\mathbf{X}$ --NumPy array or SciPy sparse matrix--, where $n$ is the
number of samples, and $p$ the number of features--, and possibly a
quantity to predict, $\mathbf{y}$, also an array, 1D unless the
prediction is \emph{multi-output}, with floats for a regression task, as
in the wages prediction, or integers for classification, that is
predicting for each sample to which class it belongs. The data seldom
come in this form, and they must be adapted to be suitable for
consumption by estimators.
Scikit-learn comes with flexible feature extraction code to solve this problem.

>>>>

\paragraph{Setting up models and feeding them data.}
%
Learning algorithms in scikit-learn are embodied in \emph{estimators}:
objects instantiated with parameters that control learning.
Data is passed to the {\tt fit} method,
which accepts an $(n \times p)$ data matrix $\mathbf{X}$,
represented as a NumPy array or SciPy sparse matrix, where $n$ is the
number of samples, and $p$ the number of features.
When there is a quantity or class label to predict,
a second argument $\mathbf{y}$ (usually a 1D array)
contains the desired outcomes for the rows in $\mathbf{X}$.
For a regression task such as wage prediction, these are real-valued,
while in classification they are integers or strings that serve as labels
for the class to which each sample belongs.
Because data seldom arrives in this format,
scikit-learn comes with flexible feature extraction code
to make data suitable for consumption by estimators.
